### 2019-02-27 docs/notebooks/results.Rmd
update results.ipynb + .Rmd

---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.0'
      jupytext_version: 1.0.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
---

@@

TEST_RESULTS_DIR = '../../data/experiment_1/results'
eff_400_results = os.path.join(TEST_RESULTS_DIR,
                            'config_efficient_400_epochs_models/test_alexnet_output.gz')
ineff_400_results = os.path.join(TEST_RESULTS_DIR,
                             'config_inefficient_400_epochs_models/test_alexnet_output.gz')

ftr_v_spt_conj(eff_400_results,
               ineff_400_results,
               epochs=400)
```

@@

```{python}
TEST_RESULTS_DIR = '../../data/experiment_2/results'
epochs_list = [10, 50, 200, 800]
eff_results_list = []
ineff_results_list = []
for epochs in epochs_list:
    eff_results = os.path.join(TEST_RESULTS_DIR, f'config_efficient_{epochs}_epochs_models/test_alexnet_output.gz')
    eff_results_list.append(eff_results)
    ineff_results = os.path.join(TEST_RESULTS_DIR, f'config_inefficient_{epochs}_epochs_models/test_alexnet_output.gz')
    ineff_results_list.append(ineff_results)
    ftr_v_spt_conj(eff_results,
                   ineff_results,
                   epochs=epochs)
```

To quantify this result, we fit slopes to the accuracy vs. set size plots for each trained replicate of AlexNet, for each number of training epochs. As shown below, the slope for feature search decreased as the number of training epochs increased, while the slpe for spatial conjunction search increased. We took the mean slope for each type of search stimulus and subtracted them to get a measure of the difference, and saw that indeed this difference did increase as the number of training epochs increased.

```{python}
mn_slope_by_epoch(eff_results_list, ineff_results_list, epochs_list)
```

>>>>

---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.0'
      jupytext_version: 1.0.1
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
---

@@

TEST_RESULTS_DIR = '../../data/experiment_1/results'
ftr_400_results = os.path.join(TEST_RESULTS_DIR,
                            'feature_search_alexnet_models/test_alexnet_trained_400_epochs.gz')
sptl_400_results = os.path.join(TEST_RESULTS_DIR,
                             'spatial_config_search_alexnet_models/test_alexnet_trained_400_epochs.gz')

ftr_v_spt_conj(ftr_400_results,
               sptl_400_results,
               epochs=400)
```

@@

```{python}
TEST_RESULTS_DIR = '../../data/experiment_1/results'
epochs_list = [10, 50, 200, 400, 800]
ftr_results_list = []
sptl_results_list = []
for epochs in epochs_list:
    ftr_results = os.path.join(TEST_RESULTS_DIR, f'feature_search_alexnet_models/test_alexnet_trained_{epochs}_epochs.gz')
    ftr_results_list.append(ftr_results)
    sptl_results = os.path.join(TEST_RESULTS_DIR, f'spatial_config_search_alexnet_models/test_alexnet_trained_{epochs}_epochs.gz')
    sptl_results_list.append(sptl_results)
    ftr_v_spt_conj(ftr_results,
                   sptl_results,
                   epochs=epochs)
```

To quantify this result, we fit slopes to the accuracy vs. set size plots for each trained replicate of AlexNet, for each number of training epochs. As shown below, the slope for feature search decreased as the number of training epochs increased, while the slope for spatial conjunction search increased. We took the mean slope for each type of search stimulus and subtracted them to get a measure of the difference, and saw that indeed this difference did increase as the number of training epochs increased.

```{python}
mn_slope_by_epoch(ftr_results_list, sptl_results_list, epochs_list)
```
